Can dike grassland restoration profit from ideal seed mixture-substrate combinations?

### 2023-02-15 manuscript.Rmd
Update manuscript.Rmd

---
title: "Development of restored dike grasslands to reference needs more than four years and can hardly modified by local site conditions"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: template_word.docx
csl: template_references_j_appl_ecol.csl
bibliography: bibliography.bib
---

# Document head (remove later) <!--# Remove --> {.unnumbered}

@@

Max 8000 words <!--# Remove -->

@@

@@

Bayesian models

dike grasslands

embankment

endangered species

environmental filter

@@

restoration

sand

soil properties

surveys

vegetation

@@

Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020]. Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@KleberLerchbaumer.2017]. Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.

>>>>

---
title: "Can dike grassland restoration profit from ideal seed mixture-substrate combinations?"
author: Markus Bauer*, Jakob Huber, Johannes Kollmann
output:
  officedown::rdocx_document:
    reference_docx: template_word.docx
csl: template_references_j_appl_ecol.csl
bibliography: bibliography.bib
---

@@

@@

Sowing is a well established restoration technique to overcome dispersal limitation. Though, adapted seed mixtures to certain site conditions promise a more effective restoration. This is especially important if the restored vegetation has to protect constructions like dikes. An ideal seed mixture-substrate combination would enhance erosion protection and species-rich grasslands.

@@

artificial soil mixture

community assembly

dry grasslands

Favorable Conservation Status

hay meadow

persistences

river embankment

soil restoration

sowing

@@

species-rich grassland

@@

Dikes are promising sites for the restoration of species-rich grasslands [@Liebrand.1996], because they can increase habitat area and connectivity of semi-natural grasslands and therefore significantly contribute to biodiversity conservation in an agricultural landscape [@Batori.2020]. Dikes have specific characteristics with strongly exposed slopes and river and land orientation [@Batori.2016] and need a reliable vegetation cover to conserve dike security [@berendse2015]. Dikes can reconcile several requirements [@teixeira2022], but the seed mixture-substrate combination must be adapted.
